---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
```

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

# fakir

The goal of {fakir} is to provide fake datasets that can be used to teach R.  

As it is designed for teaching data wrangling and data visualisation, some datasets follow the tidy-data principles, other don't. 

Supported languages are, for now, French and US English.

## Example

### Fake support ticket base : 

- All tickets
```{r}
library(fakir)
fake_ticket_client(vol = 10)
```

- Separate tickets and client databases
```{r}
tickets_db <- fake_ticket_client(vol = 100, split = TRUE)
tickets_db
ggplot(tickets_db$clients) +
  aes(entry_date, fidelity_points) +
  geom_point() +
  geom_smooth()
ggplot(tickets_db$tickets) + aes(type) + geom_bar()
ggplot(tickets_db$tickets) + aes(state) + geom_bar()
```


### Fake visits : 

```{r}
fake_visits(from = "2017-01-01", to = "2017-01-31")
```

### Fake questionnaire on mean of transport / goal

- All answers

```{r}
fake_sondage_answers(n = 10)
```

- Separate individuals and their answers
```{r}
fake_sondage_answers(n = 10, split = TRUE)
```

### fake transport use

```{r}
answers <- fake_sondage_answers(n = 30)
answers

ggplot(answers) + aes(age, log(distance_km), colour = type) + geom_point() +
  geom_smooth() + facet_wrap(~type, scales = "free_y")
```


## Prior work 

This package is heavily inspired by [{charlatan}](https://github.com/ropensci/charlatan). 

Scott Chamberlain (2017). charlatan: Make Fake Data. R package version 0.1.0.
https://CRAN.R-project.org/package=charlatan

## Contribute 

You can contribute to {fakir} in two ways: 

### Translate 

You can translate to other locales by providing : 

+ new `vec` in "R/utils"
+ new `local` in "R/fakethis"

### New dataset

Feel free to create new dataset generators.

## COC

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
