---
title: "fake client service database"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fake-client-database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center"
)
```

```{r, message=FALSE}
library(fakir)
library(dplyr)
library(ggplot2)
library(sf)
```

The database fakes an after-sale client database for a Phone company. There is: 

- a client database with all characteristics of the clients.
- a ticket database which contains all calls to the after-sale service of some clients having problems

- Ticket centered dataset with already joined client characteristics
```{r}
fake_ticket_client(vol = 10)
```

- Separate tickets and client databases
```{r}
tickets_db <- fake_ticket_client(vol = 100, split = TRUE)
tickets_db
```

- Explore datasets
```{r}
ggplot(tickets_db$clients) +
  aes(x = entry_date, y = fidelity_points) +
  geom_point() +
  geom_smooth()
ggplot(tickets_db$tickets) +
  aes(x = type) +
  geom_bar()
ggplot(tickets_db$tickets) + 
  aes(x = state) + 
  geom_bar()
```

- Join with internal {sf} spatial dataset `fra_sf`. _{sf} package must be loaded._

```{r}
clients_map <- tickets_db$clients %>% 
  group_by(id_dpt) %>% 
  summarise(
    number_of_clients = n(),
    average_fidelity = mean(fidelity_points, na.rm = TRUE)
  ) %>% 
  full_join(fra_sf, by = "id_dpt") %>% 
  st_sf()

ggplot(clients_map) +
  geom_sf(aes(fill = average_fidelity)) +
  scale_fill_viridis_c() +
  coord_sf(
    crs = 2154,
    datum = 4326
  )
```
